Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Cleanup

\todo{Check naming consistency inside sections, and across them. Possibly contain some definitions in preliminaries.}

@@

\todo{Include e-mails? Or shall we skip it for now.}

\todo{Check ACM package whitelist}

\todo{Replace package algorithmpseudocode, it is not whitelisted https://www.acm.org/publications/taps/whitelist-of-latex-packages}

\todo{Make an ACM account for the submission}

@@

\todo{Spellcheck, grammar (grammarly?)}

\todo{Make sure our manuscript is autor anonymous}

@@

\maciek{Consistency: collocated at OR collocated in OR collocated on}

\maciek{Component respecting vs component respecting. In the same way "a lower bound" and "to lower-bound"}

>>>>

@@

@@

@@

\todo{Consistency: collocated at OR collocated in OR collocated on}
